\documentclass[report,type=bsc,colorback,accentcolor=tud9c,bigchapter,bibliography=totoc,11pt]{tudthesis}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{multirow}
%\usepackage{subfig}
\usepackage{subcaption}
\usepackage{enumitem}
\usepackage[backgroundcolor=lightgray,bordercolor=white]{todonotes}
\usepackage{cellspace}
\usepackage{mdframed}
\usepackage{titlesec}
\usepackage{csquotes}
\usepackage[final]{showlabels}
\usepackage{epigraph}
% \epigraphsize{\small}% Default
\setlength\epigraphwidth{14.3cm}
\setlength\epigraphrule{0pt}


\usepackage{etoolbox}

%\titlespacing*{\chapter}{0ex}{-1cm}{1cm}

\definecolor{davysgrey}{rgb}{0.33, 0.33, 0.33}
\mdfsetup{%
	linecolor=davysgrey,
	linewidth=1pt,
	%backgroundcolor=red!10,
	roundcorner=4pt
}

\setenumerate{topsep=8pt,parsep=1pt}
\setitemize{topsep=8pt,parsep=1pt}

\setlength\cellspacetoplimit{4pt}
\setlength\cellspacebottomlimit{4pt}

\thesistitle{Text classification using concept maps}{}
\author{David Marlon Gengenbach}
\birthplace{Gemmingen-Stebbach}
\referee{Prof. Dr. Iryna Gurevych}{Prof. Dr. Kristian Kersting}%[Dr. Tobias Falke]
\department{Fachbereich Informatik}
\group{UKP Lab}
%\dateofexam{\today}{\today}
\input{assets/commands}
%numeric
\usepackage[backend=biber,style=alphabetic]{biblatex}
\addbibresource{library.bib}

\begin{document}
  \makethesistitle
  %\affidavit{David Marlon Gengenbach}
  
\chapter*{Thesis Statement}
\vskip4ex
Pursuant to \S 23 paragraph 7 of APB TU Darmstadt, I herewith formally declare that I, David Marlon Gengenbach, have written the submitted thesis independently. I did not use any outside support except for the quoted literature and other sources mentioned in the paper. I clearly marked and separately listed all of the literature and all of the other sources which I employed when producing this academic work, either literally or in content. This thesis has not been handed in or published before in the same or similar form.

I am aware, that in case of an attempt at deception based on plagiarism (\S38 Abs. 2 APB), the thesis would be graded with 5,0 and counted as one failed examination attempt. The thesis may only be repeated once.
In the submitted thesis the written copies and the electronic version for archiving are identical in content.
\vskip8ex
\noindent Darmstadt, 18th of January 2018
\vskip6ex
\noindent\tudrule[0.6\textwidth]\\
{\normalsize(David Marlon Gengenbach)}
  
  \newpage
  
  \tableofcontents
  \newpage
  \setcounter{page}{1}
  \abstract{\input{chapters/abstract}}
  \newpage
  \labelchapterinclude{Introduction}{sec:introduction}{chapters/introduction}
  \labelchapterinclude{Background}{sec:background}{chapters/background}
  \labelchapterinclude{Experimental Setup}{sec:evaluation}{chapters/evaluation}
  \labelchapterinclude{Results and Discussion}{sec:results}{chapters/results}
  \clearpage
  \labelchapterinclude{Conclusions}{sec:conclusions}{chapters/conclusions}
  %\listoftodos
  
  \newpage

  \printbibliography[heading=bibintoc]

%\vspace{3cm}
% \listoffigures
% \vspace{3cm}
% \listoftables
  
  \newpage
  \section*{Acknowledgements}
  I would like to acknowledge several people who helped me along the way.
  First, I'd like to thank Tobias Falke who gave me great support during the thesis with his answers and help structuring my thesis/work in general.
  Prof. Dr. Kristian Kersting, who provided me important hints and guided my thesis to a more scientific approach.
  My family, for their support and good words.
  Patrick Wieth and Marius Vieth, for awakening my interest in ML.
  Micha Ober, for the server he so graciously borrowed me for several months.
  Andreas Frankenberger, for providing a place for the borrowed server where it terrorized his employees with its non-bearable fan noises.
  And last but not least, the \textit{Neural Lourdes} friends for the interesting - and \textit{sometimes} even productive - discussions about ML.
  Also, thanks to all the contributers to open-source or free software who provide their work free of charge instead of creating pay-walls which arguably hinder progress in science.
  This work would not be possible in this form without open-source or free software.
  
  \vspace{0.5cm}
  \centering\textsf{\textbf{A thousand thanks to all of you!}}
\end{document}
